MCTS Based on Simple Regret

### 2012-02-21 paper/srcr/paper.tex
presentation narrative in progress

%\title{MCTS Based on Simple Regret}
%\author {David Tolpin, Solomon Eyal Shimony \\
%Department of Computer Science, \\
%Ben-Gurion University of the Negev, Beer Sheva, Israel \\
%\{tolpin,shimony\}@cs.bgu.ac.il}

\title{MCTS Based on Simple Regret}
\author {Submission 198}

@@

%\section*{Acknowledgments}

%The research is partially supported by Israel
%Science Foundation grant 305/09, by the Lynne and William Frankel
%Center for Computer Sciences, and by the Paul Ivanier Center for
%Robotics Research and Production Management.

>>>>

\title{MCTS Based on Simple Regret}
\author {David Tolpin, Solomon Eyal Shimony \\
Department of Computer Science, \\
Ben-Gurion University of the Negev, Beer Sheva, Israel \\
\{tolpin,shimony\}@cs.bgu.ac.il}

\title{MCTS Based on Simple Regret}

@@

\section*{Acknowledgments}

The research is partially supported by Israel
Science Foundation grant 305/09, by the Lynne and William Frankel
Center for Computer Sciences, and by the Paul Ivanier Center for
Robotics Research and Production Management.
